WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2014-07-24 ms.tex
Update discussion of adaptive refinement

We begin by evaluating the posterior probability density at the center of each of the $N_{\mathrm{pix},0} = 768$ pixels of an $N_{\mathrm{side},0}=8$ \ac{HEALPix} grid. At this resolution, each pixel has an area of 54\,deg$^2$. We then rank the pixels by contained probability (assuming constant probability density within a pixel), and subdivide the most probable $N_{\mathrm{pix},0}/4$ pixels into $N_{\mathrm{pix},0}$ new pixels. We then evaluate the posterior again at the pixels that we subdivided, sort again, and repeat eight times, so that we have evaluated the posterior probability density a total of $8 N_{\mathrm{pix},0}$ times. On \emph{most} iterations, we descend one level deeper in \ac{HEALPix} resolution. The resulting map is a tree structure that consists of a mix of several resolutions. We traverse the tree and flatten it into the highest resolution represented. The highest possible resolution is $N_\mathrm{side}=2^{11}$, with an area of 1.7\,deg$^2$ per pixel.\footnote{Although the resulting sky map contains $N_\mathrm{pix}=24\,576$ pixels, at most $4\,800$ pixels have distinct values. For the purpose of delivery to observers, therefore, the output is always \texttt{gzip}\nobreakdashes-compressed with a ratio of $\sim 5:1$.}

>>>>

We begin by evaluating the posterior probability density at the center of each of the $N_{\mathrm{pix},0} = 3072$ pixels of an $N_{\mathrm{side},0}=16$ \ac{HEALPix} grid. At this resolution, each pixel has an area of 13.4\,deg$^2$. We then rank the pixels by contained probability (assuming constant probability density within a pixel), and subdivide the most probable $N_{\mathrm{pix},0}/4$ pixels into $N_{\mathrm{pix},0}$ new pixels. We then evaluate the posterior again at the pixels that we subdivided, sort again, and repeat seven times, so that we have evaluated the posterior probability density a total of $8 N_{\mathrm{pix},0}$ times. On \emph{most} iterations, we descend one level deeper in \ac{HEALPix} resolution. The resulting map is a tree structure that consists of a mix of several resolutions. We traverse the tree and flatten it into the highest resolution represented. The highest possible resolution is $N_\mathrm{side}=2^{11}$, with an area of $\approx 10^{-3}$\,deg$^2$ per pixel.\footnote{Although the resulting sky map contains $N_\mathrm{pix} \approx 5\times10^6$ pixels, at most $\approx 2\times10^4$ pixels have distinct values. For the purpose of delivery to observers, therefore, the output is always \texttt{gzip}\nobreakdashes-compressed with a ratio of $\approx 250:1$.}
